%----------------------------------------------------------------------------------------
% Academic Research
%----------------------------------------------------------------------------------------

\section{\textcolor{ForestGreen}{Academic Research}}

Boston University's Mugar library maintains an impressive collection of books, articles, and electronic databases for academic research. Each of the electronic databases contain hundreds of individual journals, which, in turn, contain decades of academic research.

In addition to the instruction you receive from your professors, the Mugar library has created the following guides to aid you in the research process.

\subsection{Mugar library research guides}

\textbf{The research process}: evaluating sources, finding background information, accessing academic articles and books, using online databases: 

\url {http://www.bu.edu/library/guide/guidetoresearch/}

\textbf{Topic-based research guides}:

\url{http://www.bu.edu/library/research/guides/research-guides/}

\textbf{Other research-related how-to guides}:

\url{http://www.bu.edu/library/help/how-to/}

\subsection{Recommended electronic databases}


\textbf{JSTOR}: ``Provides page images of back issues of the core scholarly journals in the humanities, social sciences, and basic sciences from the earliest issues to within a few years of current publication. Users may browse by journal title or discipline, or may search the full-text or citations/abstracts.''

\textbf{MLA}: ``Indexes critical materials on literature, languages, linguistics, and folklore. Provides access to citations from worldwide publications, including periodicals, books, essay collections, working papers, proceedings, dissertations and bibliographies.''

\textbf{Project Muse}: ``Provides digital humanities and social sciences content for the scholarly community and is a source of complete, full-text versions of journals and monographs from many of the world's leading university presses and scholarly societies.''

\textbf{Lexis-Nexis}: ``Provides access to various databases, including current news, business information, company directories, federal and state laws, regulations, legal cases, etc..''

\textbf{Google Scholar}: ``Google Scholar provides a simple way to broadly search for scholarly literature. From one place, you can search across many disciplines and sources: articles, theses, books, abstracts and court opinions, from academic publishers, professional societies, online repositories, universities and other web sites. Google Scholar helps you find relevant work across the world of scholarly research"--Information screen (viewed Jan. 10, 2012).''

\textbf{America, History and Life}: ``Provides historical coverage of American history, including the United States and Canada from prehistory to the present. Includes information abstracted from over 2,000 journals published worldwide. Database coverage is 1964 to the present.''

\textbf{H.W. Wilson}: ``Humanities full text includes many of the most important academic journals in the humanities with the full text of articles from over 300 periodicals dating back to 1995, and high-quality indexing for almost 700 journals--of which 470 are peer-reviewed--dating as far back as 1984. The database provides coverage of feature articles, interviews, bibliographies, obituaries, and original works of fiction, drama, poetry and book reviews, as well as reviews of ballets, dance programs, motion pictures, musicals, radio and television programs, plays, operas, and more.''


\begin{quote}
[Descriptions taken from \url{http://www.bu.edu/library/research/collections/databases/} and viewed on August 22, 2012]
\end{quote}

%----------------------------------------------------------------------------------------
% END OF SECTION
%----------------------------------------------------------------------------------------
