%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\chapter{Rhetoric And Composition}


\section{What is rhetoric?}

Rhetoric is the study of oral, written, and visual persuasion. Oral speeches were an 
important part of social, political, and judicial life in ancient Greece, which gave birth 
to democratic government. Aristotle's work, \emph{The Art of Rhetoric}, is one of the 
earliest known books on the subject. For the next 2,300 years, classical rhetoric was an 
integral part of Western culture: most educated citizens were required to take classes 
in it.

\subsection{What is the purpose of rhetoric?}

Rhetoric helps us determine how to use reason, emotion, and the strength of our own 
character to persuade others to change their views. It allows us to think critically about 
how others attempt to persuade us. It further provides methods for generating, 
arranging, and styling content. It directs our attention, as writers, to the importance 
of rhetorical situations, audience awareness, and voice.

\subsection{Where can I find more online information about rhetoric?}

Try the website \href{http://rhetoric.byu.edu} {\{Silva Rhetoricae\}}, or "The Forest of 
Rhetoric," which explains the rhetorical proofs of ethos, pathos, and logos and lists and 
defines figures of speech.


\section{What is composition?}

Composition is a discipline concerned with how to write or compose language. To 
compose is to select and arrange words to achieve your purposes. There are many 
reasons to write--for example, you might write to express yourself, to entertain others, 
to persuade, to maintain contact, to clarify, or to synthesize material.

Composition classes grew out of rhetoric classes. By the mid 19th century, due to the 
increase in students attending college, rhetoric courses shifted from emphasizing 
speaking to focusing on writing. During the 1960s in America, the modern professional 
study of composition began, with an emphasis on research that explained how best to 
teach college writing.
 
\subsection{Why take a composition class?}

Writing well is crucial for success in college and in the professional world. Learning to 
compose your thoughts in language that is clear, organized, sophisticated, precise, and 
educated will allow you to communicate effectively with peers, professors, colleagues, 
and employers.


\subsection{Are there any good websites that will help me with my writing?}
Visit \href{http://owl.english.purdue.edu}{\{Purdue University's Online Writing Lab\}}, or 
OWL, which has information on formatting and common writing errors, research tips, 
worksheets and exercises.


%----------------------------------------------------------------------------------------
% END OF SECTION
%----------------------------------------------------------------------------------------
