
%----------------------------------------------------------------------------------------
%	MLA
%----------------------------------------------------------------------------------------

\subsection{MLA style} % Sub-section


\subsubsection{Formatting the MLA essay}
When setting up your word processor for an MLA-formatted document, use the following settings and rules:

\begin{itemize}
\item Set 1'' margins on all sides of the document.
\item Double-space the entire document, including block quotes.
\item Include your last name and page number on each page in the top right corner of the header.
\item In the top left portion of the first page, type your name, instructor's name, course title, and date on separate, double-spaced lines.
\item Include a centered title on the first page.
\item Indent the first line of each paragraph with a tab set to 0.5''.
\item When a quotation runs more than four typed lines, use a block quote. A block quote is a free-standing block of text, set apart from the rest of the text. Use the following four rules to format the quote: 

1) Begin the block quote on a new line. 

2) Indent every line of the quote 1'' from the left margin (two tabs). 

3) Do not use quotation marks around the quoted material. 

4) Place the parenthetical citation \emph{after} the final punctuation of the quoted passage. For example:

\begin{quote}
\textbf{Normal in-text citation:}

He argues that ``there is no such thing as `safety' scissors'' (Smith 89).

\textbf{Block quote}: 


Wolfgang Sapir explains the dangers of scissors:
\begin{doublespace}

\tab \tab Despite their comfort-inducing name, there is no such thing \\ \tab \tab as ``safety'' scissors. Running with scissors claims the lives \\ \tab \tab of hundreds of school children each year, and is statistically \\ \tab \tab one of the most dangerous threats faced by kindergartners \\ \tab\tab in all 50 states. (Sapir 89)

\end{doublespace}
\end{quote}

\end{itemize}

The following page is a model for the MLA-formatted document:

%-----------MLA FIRST PAGE EXAMPLE--------
\newpage
\thispagestyle{empty}
\begin{flushright}Johnson 1\end{flushright}
\bigskip
\begin{doublespace}
Jeff Johnson\\
Profesor Smith\\
English 130\\
January 28, 2010
\end{doublespace}
\begin{center}
America's Foreign Policy Future?
\end{center}
\begin{doublespace}

\tab While all of the world may indeed be a stage, we must be decisive in the measures we take in order to prevent the curtain from closing too soon. We currently live in an era of great political uncertainty. After the Cold War, America suddenly became the stand-alone world power, dominating international treaties, coalitions, and movements. This ``unipolarity'' has resulted in one of the most wholly economically prosperous and peaceful periods of time in history. The coexistence and international functionality that we enjoyed during the 90s for a large part can be credited to the United States' influential methods of maintaining world order.
\end{doublespace}
\newpage
%------DONE------------------

\subsubsection{In-text citations}
The MLA style uses parenthetical citations to indicate the author and page number of sources. These parenthetical citations take two forms. The first form is used when the source you are citing \emph{is known or understood} by your audience. The second form is used when the author being cited is \emph{unknown or unclear}. 

In the following sentence, the author of the source in question is obvious:

\begin{quote}According to scholar James Frey, ``Americans eat five pounds of ice cream annually" (78).
\end{quote}

Since the author, James Frey, is understood, the citation uses \textbf{only the page number} of the source.

In these versions of the sentence, however, the author is not stated:

\begin{quote}
According to one scholar, ``Americans eat five pounds of ice cream annually" (Frey 78).
\end{quote}
Or:

\begin{quote}
Studies have shown that the American people consume an average of five pounds of ice cream every year (Frey 78).
\end{quote}
In the first sentence, the author is referred to only as a generic ``scholar.'' To give the reader information on which scholar is being cited, Frey's name is included in the citation. In the second sentence, the author describes the report, not its author; as a result, the student has included Frey's name to indicate whose report is being referenced. 

%----DONE-----------

\subsubsection{Bibliography}

MLA requires a bibliography at the conclusion of the essay that includes the full citation of the sources cited within the essay. In MLA, the bibliography is known as the Works Cited page. When setting up a Works Cited page, use the following rules and characteristics:

\begin{itemize}
\item Center the words ``Works Cited'' at the top of the page.
\item Use your last name and the page number on the right side of the page's header.
\item Double-space the Works Cited entries.
\item Alphabetize the entries by the author's last name.
\item If an entry runs more than one typed line, indent the second (and any subsequent) line with a .5'' tab.
\item If two or more works by the same author are used, list the entries alphabetically by title. After the first entry, replace the author's name with three dashes followed by a period. (See the entries from St. Augustine on the following page).
\end{itemize}


Here is an example of a MLA formatted Works Cited page:

%-----------MLA Works Cited EXAMPLE--------
\newpage
\thispagestyle{empty}
\begin{flushright}Johnson 23\end{flushright}
\begin{center}
Works Cited
\end{center}
\begin{doublespace}

Adams, Robert M. \emph{James Joyce: Common Sense and Beyond}. Woodward: Classic \tab Nonfiction Library, 1967. Print.

Augustine. \emph{Tractates on the Gospel of John}. Trans. J. W. Rettig. Washington D.C.: \tab Catholic U 
of America P, 1988. Print.

- - -. \emph{Confessions}. Trans. Henry Chadwick. New York: Oxford UP, 1992. Print.

Carver, Craig. ``Molly: Bloom's Preservative; Correspondence and Function in \tab\emph{Ulysses}.'' \emph{James Joyce Quarterly} 12 (1975): 414-22. Print.

Garrett, Peter K. Introduction. \emph{Twentieth Century Interpretations of} Dubliners. \tab Ed. Peter K. Garrett. New York: Penguin, 1968. 1-17. Print.

\end{doublespace}

\newpage




%------DONE------------------
										                



Although there are hundreds of MLA forms for citing everything from books to email conversations, they may all be reduced to two basic forms. Let's call them ``book'' and ``periodical.'' All of the other forms are merely variations of these two.

\subsubsection{Book form}


\begin{quote}
{\bf Last Name, First Name. \emph{Title}. City: Publisher, Year. Medium \tab of Publication (Web or Print).}
\end{quote}

\medskip
\medskip

\begin{quote}
Taylor, Alan. \emph{William Cooper's Town: Power and Persuasion on the \tab Frontier of the Early American Republic}. Penguin Books, 2001. \tab Print.
\end{quote}

Variations on this form include a {\bf book by multiple authors}, a {\bf book with an editor}, a {\bf translated book}, an {\bf edition}, and so on. Each of these additional forms will require slight alterations or additions to the basic form. 

\subsubsection{Commonly used book forms}

\textbf{A book with an editor}: 
\begin{quote}
James, Henry. \emph{Portrait of a Lady}. Ed. Leon Edel. Boston: Houghton, \tab 1963. Print.
\end{quote}

\textbf{A book with a translator}: 
\begin{quote}
McDougle, Astrid. \emph{The Basics of Gaelic}. Trans. Paddy Maloney. New \tab York: Vintage, 1990. Print.
\end{quote}


\textbf{An edition (other than the first)}:
\begin{quote}
Thompson, Fred. \emph{Why I Fight}. 3rd ed. New York: Vanity Publications, \tab 2000. Print.
\end{quote}

\textbf{An anthology}: 
\begin{quote}
Savage, Fred, ed. \emph{American Literature about the Great Depression}. 12th \tab ed. New York: Longman, 2012. Print.
\end{quote}

\textbf{A work in an anthology}: 
\begin{quote}
Smith, Noel. ``The Dustbowl Aesthetic.'' \emph{American Literature about the \tab Great Depression}. Ed. Fred Savage. 12th ed. New York: Longman, \tab 2012. Print.
\end{quote}

\textbf{A republished book}: 
\begin{quote}
James, Esther. \emph{My Life}. 1946. New York: Random House, 2001. Print.
\end{quote}


\subsubsection{Periodical form}
\begin{quote}
\textbf{Last Name, First Name. ``Title.'' Journal Name Volume.Issue \tab (Year): Page Number range. Medium of Publication.}
\end{quote}
\medskip
\medskip
\begin{quote}
Luck, Chad. ``Re-Walking the Purchase: \emph{Edgar Huntly}, David Hume, and \tab the Origins of Ownership.'' \emph{Early American Literature} 44.2 (2009): \tab 271-306. Print.
\end{quote}

Common variations on the basic periodical form include a \textbf{newspaper article}, an \textbf{essay in a scholarly journal}, an \textbf{essay in a collection or edited volume}, an \textbf{article in a magazine}, and an \textbf{article on a website}.

\subsubsection{Commonly used periodical forms}

\textbf{An article in a scholarly journal with volume and issue numbers}:
\begin{quote}
Taylor, James. ``The Indian Matter of Charles Brockden Brown's \emph{Edgar \tab Huntly}.'' \emph{American Literature} 45.6 (1998): 432-45. Print.
\end{quote}


\textbf{An article in a scholarly journal with only volume numbers}:
\begin{quote}
Johnston, Johanna. ``A Reading of \emph{Moby Dick}.'' \emph{North Dakota Quarterly} \tab 45 (1978): 45-56. Print.
\end{quote}

\textbf{An article in a newspaper}:
\begin{quote}
McKinley, Robert. ``Cat Saved from Dog.'' \emph{New York Times} 7 Oct. 2011: \tab A12+. Print.
\end{quote}

\textbf{An article in a magazine}:
\begin{quote}
Smith, Jim. ``Remembering Tony.'' \emph{New Yorker} Jan. 2010: 12-18. Print.
\end{quote}

\textbf{An article in an online database}:
\begin{quote}
Taylor, Hayden. ``\emph{Moby Dick} and the Cold War.'' \emph{American Literature} \tab 45.6 (2010): 45-57. 
JSTOR. Web. 12 July 2012.
\end{quote}

%----------------------------------------------------------------------------------------
% END OF SECTION
%----------------------------------------------------------------------------------------