%----------------------------------------------------------------------------------------
% Parallel Structure
%----------------------------------------------------------------------------------------
\chapter{Parallel Structure}

\section{What is it?}

Parallel structure is a way to construct your sentences so that related ideas and items 
in a series are presented in the same grammatical form.

\section{Why employ it?}

It helps indicate connections between your ideas, and thus improves the flow and 
coherence of your paper.

It can help you emphasize certain points and make them more memorable.

\section{Where should I use it?}

Parallel structure may be used in any part of your essay where you want to draw 
connections between a pair or series of ideas. It can often be used to great effect in a 
thesis statement since it is a place where you describe connections between ideas or 
points. As you may see in the following examples, parallel structure can be used to make 
striking and memorable statements:

\textbf{Instead of}: "Kissing can communicate a lot of different things." 

\textbf{Try this}: "A kiss can be a comma, a question mark, or an exclamation point." 
\textemdash Mistinguett

\textbf{Instead of:} "We shouldn't always just be thinking about ourselves and what 
we want from our government. Why don't we ever think about what we can be doing to help it"?

\textbf{Try this}: "Ask not what your country can do for you, but what you can do for 
your country." \textemdash JFK

\textbf{Instead of}: "We went fishing and hiking. And then we went for a bike ride."

\textbf{Try this}: "We went fishing, hiking, and biking."

\textbf{Instead of}: "Conversing with John Updike is kind of like it is when you go somewhere new:
                    proceed with caution."

	\textbf{Try this}: "To converse with John Updike is to enter uncharted territory: proceed with
                              caution."

\textbf{Instead of}:  "Writing well involves drafting, reviewing, and the need to edit your sentences."
 
	\textbf{Try this}: "Writing well involves drafting, reviewing, and editing."

\textbf{Instead of}: "She was a strong student and in leading other students she was good."

\textbf{Try this}: "She was not only a strong student but a good leader."

 
 %----------------------------------------------------------------------------------------
% END OF SECTION
%----------------------------------------------------------------------------------------

